\section{How to Increase Your Motivation to Practice Guitar}
Are you currently having trouble finding the motivation to practice guitar? If so, you are certainly not alone. All guitar players struggle to maintain high levels of motivation for guitar practice at one point or another.\\
In order to help you increase your motivation, we have created a list of the 5 most common reasons why guitar players are unable to get great results when they practice guitar.
\subsection*{Reason 1: Not Sure What Needs To Be Practiced On Guitar}
The majority of guitar players do not know exactly what they should be practicing and why they should be practicing it. This causes them to attempt learning as many new exercises on guitar as possible without any direction.\\
By practicing so many different ideas for guitar at once, it is easy to become overwhelmed. This happens because most guitar players simply do not give themselves enough time to fully process all the new information they are learning.\\
If you are unsure about what you need to learn on guitar, it will eventually become difficult to maintain your motivation for guitar practice. To solve this, think about your goals as a musician, then make a list of the items you need to learn to reach those goals. These items should be the big picture focus around which your practice sessions are based.
\subsection*{Reason 2: Unorganized And Ineffective Practicing Habits}
Most guitarists practice in a totally unorganized and ineffective manner. Unfortunately, they are usually unaware of this and go for weeks, months, or even years at a time using the same ineffective guitar practice methods!\\
One example of a commonly used, yet ineffective method is the idea of using an equal amount of time on every task in your guitar practice. This is just like trying to prepare a dish by using an equal amount of ingredients without thinking about how each of the ingredients will affect the taste of the food. This guitar practice method will cause you to spend too much time on things that are not important to your overall guitar playing progress.\\
Another mistake that guitarists make during their guitar practice is that they spend a lot of time focusing on the guitar skills they WANT to practice rather than the guitar skills that they NEED to practice in order to achieve their musical goals. This causes their guitar playing skills to become imbalanced. As a result, their weak areas tend to hold back their ability to apply their well developed skills in musical situations.\\
In order to make progress in your guitar playing, it is essential to learn how to correctly allocate your time among your practice items.
\subsection*{Reason 3: Not Having Fun With Guitar Practice}
Many guitar players have conditioned themselves to believe that guitar practice is nothing more than a boring set of repetitive tasks. If you have this mindset, you are truly misunderstanding the basic idea behind guitar practice.\\
In order to gain motivation to practice your instrument, you must learn how to create an effective practice schedule that helps you enjoy the learning process as you work toward your guitar playing goals. Once you obtain the right tools to create a such a highly productive and inspirational practice schedule, you will find it much easier to have fun with the time you spend practicing guitar.\\
As time goes on, you will begin treating guitar practice as an opportunity to improve on your instrument in order to play music the way you always wanted rather than as a mere obligation that you must complete each day.\\
\subsection*{Reason 4: Not Focusing Enough On Long Term Goals}
It takes many years to become a great guitar player. If you want to become a great guitarist, you must clearly determine the best paths to take in order to achieve your long term goals. Once you have clearly identified your long term music goals, you will need to focus on using your guitar practice time effectively to reach them.\\
To do that, think of your guitar practice sessions as individual pieces of a puzzle that make up the big picture of your musical goals. The better you understand the big picture of your guitar practice, the easier it will be to create effective guitar practice schedules. Additionally, as you begin to "put together the puzzle" and make progress you will become more motivated to practice guitar.
\subsection*{Reason 5: Losing Motivation Due To Lack Of Quick Progress}
Even if you understand the best way to effectively practice guitar, you will not achieve big results overnight. Many guitar players expect instant results when using a new practice method. Unfortunately, when they do not get the quick results they are looking for, they end up abandoning (what might be) a truly effective guitar practice method.\\
This results in inconsistent guitar playing progress since you do not give yourself the time to get the benefits from the guitar practice methods you use. This approach to guitar practice is like reading ten different books and stopping a few pages into each one before you have time to understand the story. While practicing guitar, give each method time to work (or not work) before deciding to move on to something else.
\subsection*{What Should You Do Next?}
After reading this article, you should have a better understanding of why you have a hard time staying motivated in your guitar practice. Think about how the guitar practice solutions mentioned above can apply to your current practice routine. Even though this article has only touched on a few of the problems that you might face as you develop your guitar skills, your guitar playing will benefit greatly by applying them in your everyday practice.\\
Good luck and happy practicing!

\em{from Ultimate Guitar Tabs \& Chords 29-12-2015}
